---
title: "Practice Survey Analysis"
format:
  html:
    toc: true
execute:
  warning: false
  message: false
---

```{r}
library(tidyverse)
library(tidytext)
library(gtsummary)
```

## Study context

This practice survey includes one participant per profession. We combine:

- Open-text answers (qualitative, text-mining view)
- Multiple-choice questionnaire answers (quantitative)

```{r}
participants <- tibble(
  participant_id = paste0("P", 1:6),
  profession = c("Hematologist", "Nurse", "Pharmacist", "Biologist", "Data Manager", "Resident")
)

likert_levels <- c("Low", "Medium", "High")

open_text <- tribble(
  ~participant_id, ~question, ~response,
  "P1", "Main challenge", "Coordinating urgent transfusion decisions with complete patient context",
  "P1", "What helps", "Shared protocols and quick multidisciplinary discussions",
  "P1", "Improvement priority", "Better digital tracking of blood product availability",
  "P2", "Main challenge", "High workload and rapid symptom monitoring during treatment",
  "P2", "What helps", "Team communication and clear bedside checklists",
  "P2", "Improvement priority", "More time for patient education and discharge planning",
  "P3", "Main challenge", "Stock constraints and treatment adaptation in real time",
  "P3", "What helps", "Early prescription review and pharmacy-clinic coordination",
  "P3", "Improvement priority", "Automated alerts for interactions and shortages",
  "P4", "Main challenge", "Interpreting complex biomarkers for therapy selection",
  "P4", "What helps", "Standardized reporting and close clinician feedback",
  "P4", "Improvement priority", "Faster sample logistics and integrated data pipelines",
  "P5", "Main challenge", "Linking fragmented data across clinical systems",
  "P5", "What helps", "Structured data entry and shared data dictionaries",
  "P5", "Improvement priority", "Dashboards for outcomes and operational indicators",
  "P6", "Main challenge", "Balancing training needs with daily patient flow",
  "P6", "What helps", "Mentorship and practical decision support tools",
  "P6", "Improvement priority", "Protected learning time and simulation sessions"
)

questionnaire <- tibble(
  participant_id = paste0("P", 1:6),
  confidence_guidelines = factor(c("High", "Medium", "High", "Medium", "Medium", "Low"), levels = likert_levels, ordered = TRUE),
  digital_tools_satisfaction = factor(c("Medium", "Low", "Medium", "High", "Medium", "Low"), levels = likert_levels, ordered = TRUE),
  interdisciplinary_meetings = c("Weekly", "Weekly", "Monthly", "Monthly", "Weekly", "Weekly"),
  training_need = c("Yes", "Yes", "No", "Yes", "No", "Yes")
)

survey_data <- participants %>%
  left_join(questionnaire, by = "participant_id")
```

## Text-mining of open responses

```{r}
min_token_length <- 3
top_n_terms <- 3
stop_words_local <- tidytext::stop_words %>% distinct(word)

tokens <- open_text %>%
  left_join(participants, by = "participant_id") %>%
  mutate(
    response = str_to_lower(response),
    response = str_replace_all(response, "[^a-z0-9\\s-]", " "),
    response = str_squish(response)
  ) %>%
  unnest_tokens(word, response, token = "words") %>%
  filter(nchar(word) >= min_token_length) %>%
  anti_join(stop_words_local, by = "word")

tokens %>%
  count(word, sort = TRUE) %>%
  slice_head(n = 10)
```

```{r}
tokens %>%
  count(profession, word, sort = TRUE, name = "freq") %>%
  group_by(profession) %>%
  slice_max(freq, n = top_n_terms, with_ties = FALSE) %>%
  ungroup() %>%
  ggplot(aes(x = reorder(word, freq), y = freq, fill = profession)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~profession, scales = "free_x") +
  labs(
    title = "Top recurring terms by profession",
    x = "Term",
    y = "Count"
  ) +
  coord_flip()
```

## Multiple-choice questionnaire comparison

Because this is a practice dataset with one participant per profession, the table below is shown overall (not stratified).

```{r}
survey_data %>%
  select(profession, confidence_guidelines, digital_tools_satisfaction, interdisciplinary_meetings, training_need) %>%
  tbl_summary(statistic = all_categorical() ~ "{n} ({p}%)") %>%
  add_n() %>%
  bold_labels()
```
